A family of accessibility measures derived from spatial interaction principles

### 2025-05-18 paper/manuscript.qmd
table 8 and conclusion

In this section, we introduce a family of accessibility measures inspired by Wilson's spatial interaction modelling framework.

@@

<!-- rafa 4: there is no $X$ in equation 23-->

@@

<!-- rafa 4: there is no $X$ in equation 23-->

@@

@@

And as a summary: each member of the family of accessibility measure is named, explained in plain language, alongside their balancing factor, proportional allocation factor and mathematical equation and value interpretations in Table 8. <!-- @tbl:summary-family-of-accessibility-measures.-->

>>>>

In this section, we introduce a family of accessibility measures inspired by Wilson's spatial interaction modelling framework. At the end of this section, Table 8 presents a summary, where each member of the family of accessibility measure is explained in plain language, alongside their balancing factor, proportional allocation factor and mathematical equation and value interpretations.

@@

<!-- rafa 5: there is no $X$ in equation 23-->

@@

@@

<!-- rafa 6: glad to see that the paragraphs below use Figure 2 as an explanation aid. The text/explanation you sent me in your last email was quite helpful -->

@@

<!-- rafa 7: final paragraph with take aways -->
666666

In summary, building on @wilson1971's foundational work, this paper proposed a unified framework for accessibility that is able to account for competition. By reintroducing Wilson's proportionality constant, the proposed family of constrained accessibility measures restores measurement units to accessibility estimates. This enhancement provides a more interpretable, consistent, and theoretically grounded basis for accessibility analysis, which could help advance the adoption of accessibility-oriented planning.
